Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is a merged and final version of two conference papers, \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}, with a unified and streamlined presentation.}

### 2020-12-20 journal paper/journal_main.tex
Changed the date, removed a \newpage.
Added a \newpage elsewhere!
Updated the date.
Revised the title note.

\title{\vspace{-12mm}Competing Bandits:\\
The Perils of Exploration under Competition%
\thanks{This is a merged and final version of two conference papers,
\citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19},
with a unified and streamlined presentation and expanded related work and background materials. All theoretical results are from \citet{CompetingBandits-itcs18}, and all numerical simulations are from \citet{CompetingBandits-ec19}. Appendices~\ref{app:bg},\ref{app:examples} are completely new compared to the conference versions. We would like to thank Ian Ball, Yeon-Koo Che, Glen Weyl and Sven Rady, as well as seminar participants at Columbia and conference participants at Innovations in Theoretical Computer Science 2018, ACM Economics and Computation 2019 and the MIT Conference on Digital Experimentation 2020, for helpful comments and conversations. All errors are our own.} }
% \textit{Competing Bandits: Learning under Competition}, at Innovations in Theoretical Computer Science 2018, and \textit{The Perils of Exploration under Competition: A Computational Modeling Approach}, at ACM Economics and Computation 2019.}}

\author{Guy Aridor
\footnote{Columbia University, Department of Economics. Email: g.aridor@columbia.edu}
\and \hspace{-0.75cm}
\rule{0.0in}{0pt}
Yishay Mansour
\footnote{Google and Tel Aviv University, Department of Computer Science. Email: mansour.yishay@gmail.com}
\and \hspace{-0.75cm}
\rule{0.0in}{0pt}
Aleksandrs Slivkins%
\footnote{Microsoft Research New York City. Email: slivkins@microsoft.com}
\and \hspace{-0.75cm}
\rule{0.0in}{0pt}
Zhiwei Steven Wu%
\footnote{Carnegie Mellon University, Pittsburgh, PA.
Email: zstevenwu@cmu.edu.\newline
Research done when Z.S. Wu was an intern and a postdoc at Microsoft Research NYC.}
}
\date{First version: July 2020\\ This version: September 2020}

@@

\newpage
\section{Theoretical results: the \TheoryModel}
\label{sec:theory}
\subfile{content/sec-theory}

>>>>

\title{\vspace{-12mm}Competing Bandits:\\
The Perils of Exploration under Competition%
\thanks{This is a merged and final version of two conference publications,
\citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19},
with a unified and streamlined presentation and expanded related work and background materials. All theoretical results are from \citet{CompetingBandits-itcs18}, and all numerical simulations are from \citet{CompetingBandits-ec19}. Appendices~\ref{app:bg},\ref{app:examples} are completely new compared to the conference versions.\newline \indent 
We would like to thank Ian Ball, Yeon-Koo Che, Glen Weyl and Sven Rady for helpful comments and conversations. Likewise, we thank the audience of the conference and seminar talks on this work.
%seminar participants at Columbia and conference participants at Innovations in Theoretical Computer Science 2018, ACM Economics and Computation 2019 and the MIT Conference on Digital Experimentation 2020, for helpful comments and conversations.
All errors are our own.}}
% \textit{Competing Bandits: Learning under Competition}, at Innovations in Theoretical Computer Science 2018, and \textit{The Perils of Exploration under Competition: A Computational Modeling Approach}, at ACM Economics and Computation 2019.}}

\author{Guy Aridor
\footnote{Columbia University, Department of Economics. Email: g.aridor@columbia.edu}
\and \hspace{-0.75cm}
\rule{0.0in}{0pt}
Yishay Mansour
\footnote{Google and Tel Aviv University, Department of Computer Science. Email: mansour.yishay@gmail.com}
\and \hspace{-0.75cm}
\rule{0.0in}{0pt}
Aleksandrs Slivkins%
\footnote{Microsoft Research New York City. Email: slivkins@microsoft.com}
\and \hspace{-0.75cm}
\rule{0.0in}{0pt}
Zhiwei Steven Wu%
\footnote{Carnegie Mellon University, Pittsburgh, PA.
Email: zstevenwu@cmu.edu.\newline
Research done when Z.S. Wu was an intern and a postdoc at Microsoft Research NYC.}
}
\date{First version: July 2020\\ This version: December 2020}

@@

%\newpage
\section{Theoretical results: the \TheoryModel}
\label{sec:theory}
\subfile{content/sec-theory}
